\documentclass[a4paper,10pt]{article}

\usepackage[left=0.7in,right=0.7in,top=0.6in,bottom=0.6in]{geometry}
\usepackage{paracol}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}
\usepackage{fontawesome5}

% ---------- Colors ----------
\definecolor{darkgray}{RGB}{60,60,60}
\definecolor{midgray}{RGB}{110,110,110}
\definecolor{lightgray}{RGB}{180,180,180}

% ---------- Section style ----------
\titleformat{\section}
  {\large\bfseries\color{darkgray}}
  {}
  {0em}
  {}
  [\vspace{2pt}\color{lightgray}\titlerule]

% ---------- Lists ----------
\setlist[itemize]{
  leftmargin=1.2em,
  itemsep=2pt,
  topsep=2pt
}

% ---------- Column gap ----------
\setlength{\columnsep}{1.2cm}

\pagestyle{empty}

\begin{document}

% ---------- Header ----------
\begin{center}
    {\Huge\bfseries Luka Ivanković} \\[4pt]
    {\color{midgray}
    \faPhone\ (385) 91 538 8467 \quad
    \faEnvelope\ \href{mailto:ivkalu@gmail.com}{ivkalu@gmail.com} \quad
    \faGithub\ \href{https://ivkalu.github.io/}{ivkalu.github.io}
    }
\end{center}

\vspace{6mm}

% ---------- Two Columns ----------
\columnratio{0.68}
\begin{paracol}{2}

% ===== LEFT COLUMN (WIDE) =====
\section*{Work Experience}

\textbf{Alfatec} - Data Scientist \hfill {\color{midgray}Oct 2025 -- Present}
\begin{itemize}
    \item Integrated state-of-the-art technologies into an automated computer vision training pipeline.
    \item Worked on AI PDF-processing tool for automating workflow and saving time.
    \item Trained LSTMs and other models for time-series analysis.
\end{itemize}

\vspace{2mm}

\textbf{TensorPix} - Full-stack Engineer \hfill {\color{midgray}May 2023 -- May 2025}
\begin{itemize}
    \item Engineered and deployed an audio denoising ML model into production.
    \item Built a video reencoding and compression tool.
    \item Advanced git with automated testing tools across multiple projects.
\end{itemize}

\vspace{2mm}

\textbf{Ericsson Nikola Tesla} - Developer \hfill {\color{midgray}Oct 2022 -- Feb 2023}
\begin{itemize}
    \item Radio software development using Java and C++.
\end{itemize}

\vspace{4mm}

\section*{Projects}

\begin{itemize}
    
    \item Created a full web app for splitting audio stems with a distributed infrastructure and custom ML models on GCP. Built an audio reencoding tool.
   
    \item Fine-tuned embedding models and implemented three variations of a Retrieval-Augmented Generation (RAG) system, conducting comparative analyses of different retrieval methods, ultimately arriving at an agentic AI approach that delivered the best performance chatbot integrated into an existing financial application.

    \item Developed an online platform for D\&D players to upload campaign files, including a Claude-code-inspired AI agent that generates new sessions and assists users in managing their files

    \item Designed a PDF Reconstructor Agent and PDF Analyzer Agent that collaboratively reconstruct original documents using LaTeX with high fidelity.

    \item CycleGAN trained on 1,193 Monet paintings for unpaired artistic style transfer.

\end{itemize}

\vspace{4mm}

\section*{Competitions}

\begin{itemize}

     \item \textbf{Lumen Data Science} - Trained CV models to classify musical instruments from spectrograms (90\% accuracy).

    \item Winner of \textbf{AI Battlegrounds Hackathon 2023}; participant in Algotrade Hackathon 2024.

    \item National Competition in Algorithms 2017; 11th place, 2018; 6th place

\end{itemize}

\switchcolumn

% ===== RIGHT COLUMN (NARROW) =====
\section*{Technologies}
\color{midgray}
Python, PyTorch, Django \\
Huggingface, Vllm, Scikit-learn \\
JavaScript, TypeScript, Vue.js \\
Nuxt.js, GCP, AWS \\
Linux, Git, Docker, LangGraph \\

\vspace{4mm}

\section*{Education}
\color{midgray}
\textbf{Faculty of Electrical Engineering and Computing} \\
2019 -- 2025

\vspace{2mm}
\textbf{M.Sc. Thesis} \\
Emulation of Guitar Effects Using Machine Learning

\vspace{2mm}
\textbf{B.Sc. Thesis} \\
Deep Learning for Symbol Recognition inside Computer Game

\vspace{2mm}
\section*{Relevant Coursework}
Artificial Intelligence, Digital Image Processing, Deep Learning (I \& II), Neural Networks, Computer Vision, Machine Learning

\vspace{4mm}

\section*{Interests}
\color{midgray}
Guitar (8+ years), Piano \\
Street workout, Cycling \\
D\&D, Catan

\end{paracol}

\end{document}
